### 2023-04-11 my_paper/tables/tab03-summary-stats.tex
edit tables for presentation

\caption{Children's outcome using parent's place of birth \label{tab:c&p1}}

@@

\hspace{1em}Total Household seducation (Total Years) & \specialcell{25.78\\(4.08)} & \specialcell{23.35\\(6.51)} & \specialcell{22.19\\(6.69)} & \specialcell{17.54\\(7.83)} & \specialcell{-4.13\\(0.02)} & \specialcell{0.51\\(0.04)}\\

@@

\hspace{1em}Men’s Employment Rate & \specialcell{0.95\\(0.22)} & \specialcell{0.94\\(0.23)} & \specialcell{0.92\\(0.26)} & \specialcell{0.93\\(0.26)} & \specialcell{-0.02\\(0)} & \specialcell{-0.02\\(0)}\\
\hspace{1em}Women’s Employment Rate & \specialcell{0.96\\(0.2)} & \specialcell{0.95\\(0.22)} & \specialcell{0.93\\(0.25)} & \specialcell{0.94\\(0.24)} & \specialcell{-0.02\\(0)} & \specialcell{-0.02\\(0)}\\

>>>>

\caption{Summary statistics of outcomes using parent's place of birth \label{tab:c&p1}}

@@

\hspace{1em}Total Household seducation (Total Years) & \specialcell{25.78\\(4.08)} & \specialcell{23.35\\(6.51)} & \specialcell{22.19\\(6.69)} & \specialcell{17.54\\(7.83)} & \specialcell{-8.25\\(0.03)} & \specialcell{-1.16\\(0.07)}\\

@@

\hspace{1em}Men’s Employment Rate & \specialcell{0.95\\(0.22)} & \specialcell{0.94\\(0.23)} & \specialcell{0.92\\(0.26)} & \specialcell{0.93\\(0.26)} & \specialcell{-0.02\\(0.00)} & \specialcell{-0.02\\(0.00)}\\
\hspace{1em}Women’s Employment Rate & \specialcell{0.96\\(0.2)} & \specialcell{0.95\\(0.22)} & \specialcell{0.93\\(0.25)} & \specialcell{0.94\\(0.24)} & \specialcell{-0.02\\(0.00)} & \specialcell{-0.02\\(0.00)}\\
